Model Search in Relational Domains

### 2016-10-22 paper.tex
nudge abstract

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known Conflict-Driven Clause Learning (CDCL) algorithm that is
used in SAT solvers.  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in satisfiability 
solvers can be rather easily lifted from the Boolean lattice to other 
non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial liftings of the model search and
conflict analysis algorithms for relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser over a template polyhedra domain to check safety
properties of C programs.  We evaluate the performance of our analyser in
comparison with program verifiers that uses propositional-level solvers and
a static analysis tool.
%
Experimental evidence suggest 
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
a reduction of two orders of magnitude in the number of 
decisions and conflict analyses compared to a satisfiability 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}

>>>>

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known Conflict-Driven Clause Learning (CDCL) algorithm that is
used in SAT solvers.
\Omit {  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
}
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in satisfiability 
solvers can be rather easily lifted from the Boolean lattice to other 
non-relational domains, application to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial liftings of the model search and
conflict analysis algorithms for relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser over a template polyhedra domain to check safety
properties of C programs.  We evaluate the performance of our analyser in
comparison with program verifiers that uses propositional-level solvers and
a static analysis tool.
%
Experimental evidence suggest 
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
a reduction of two orders of magnitude in the number of 
decisions and conflict analyses compared to a satisfiability 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}
